---
output: 
  pdf_document:
    keep_tex: true
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: D:\\Dropbox\\Michiel_research\\Templates\\r-markdown-templates\\svm-latex-ms.tex
title: "Assessing maize yield gaps in Nigeria"
subtitle: "Check"
thanks: "**Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: michiel.vandijk@wur.nl."
author:
- name: Michiel van Dijk
  affiliation: Wageningen Economic Research & IIASA
- name: Zuzana Smeets Kristkova
  affiliation: Wageningen Economic Research
- name: Tom Morley
  affiliation: Wageningen Economic Research
  
abstract: "NGA MAize yield gaps abstract"
keywords: "Yield Gap"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
# spacing: double
bibliography: M:/My Documents/bibTex/library.bib

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```




# Introduction




# Background


# Methodology

We use a stochastic frontier production function [@Aigner1977; @Meeusen1977] to estimate the technical efficiency yield gap. The model is specified as follows for our study:


\begin{equation}
\label{sfa}
y_i=x_i\beta+v_i-u_i
\end{equation}

where, $y_i$ is the logarithm of actual yield (ya) for maize plot $i$, $x_i$ is a vector containing growth defining, growth limiting and growth reducing factors a set of control variables, $\beta$ is a vector of parameters, $v_i$  is a symmetric random error and $u_i$ is non-negative random variable with a half normal distribution that measures technical inefficiency. The error terms $v_i$  and $u_i$ will be influenced by unobserved household and plot-specific effects, such as farmers’ management skills and soil quality, which are correlated with some of the explanatory variables, such as for example fertilizer application. Simply pooling the data for the two survey years will result in coefficients that are biased (Hausman and Taylor, 1981). 

# Data

# Results

# Conclusions



## R Markdown


```{r cars}
summary(cars)
```

## Including Plots


```{r pressure, echo=FALSE}
plot(pressure)
```

# References
